Response to reviewers

### 2022-02-09 response/response1.Rmd
Table 2 fix, added to response
update to response

We thank the Editor and the three reviewers for their comments, which have helped substantially to improve the manuscript. In response, we have made a major revision of the main manuscript as outlined below.

@@

The editor and reviewers suggest reframing so that readers can help their students to experience the journal from wild to textbook data and either emphasize the case study, for the paper to be a regular submission for JSDSE, or to better explain the relevance for  teachers and/or students in statistics and data science to be considered for the special issue. We have chosen to do the latter, because we hope that the paper fits into the goals of the special issue.

\begin{description}
\item[Reviewer 1:] \textcolor{violet}{How is this manuscript relevant for teachers and/or students in statistics and data science?}

@@

@@

* We have corrected all minor grammatical errors pointed out by the reviewers as outlined below. [ADD the changes]  
* We have made the descriptions of the steps more explicit as follows [LIST OF THE CHANGES]

@@

We agree that this level of precision was not necessary. We have modified Table 2 in line with this.

>>>>

We thank the Editor, Associate Editor and the three reviewers for their extensive comments, which have helped substantially to improve the manuscript. In response, we have made a major revision of the main manuscript as outlined below.

@@

The editors and reviewers suggest reframing so that readers can help their students to experience the journal from wild to textbook data and either emphasize the case study, for the paper to be a regular submission for JSDSE, or to better explain the relevance for teachers and/or students in statistics and data science to be considered for the special issue. We have chosen to do the latter, because we hope that the paper fits into the goals of the special issue.

\begin{description}
\item[Editor and Reviewer 1:] \textcolor{violet}{How is this manuscript relevant for teachers and/or students in statistics and data science?}

@@

\item[Reviewer 1:] \textcolor{violet}{I don't see the direct relevance of this manuscript with the readership of JSDSE. I think this could be a valuable paper to describe the author(s) R package and would have value for researchers using the NLSY79 dataset. I am not convinced that JSDSE is the appropriate venue for this. I do not see this manuscript being engaging enough to be used in the classroom as a case study in data cleaning.}

It is commonly said 80\% of a data analysts/scientist's work is on data cleaning/preperation so we believe that shedding more light in this aspect of work is an important for students to be aware of. We believe that there are often subjective decisions made in the process (as we have done) which can be used as a conversation for transparency and reproducibility in class based on a real case study.

@@

* We have corrected all minor grammatical errors pointed out by the reviewers as outlined below:

\begin{description}
\item[Reviewer 1:] \textcolor{violet}{
\begin{itemize}
\item p2 l16: It's unclear from context what is being referred to from the Huebner et al 2020 citation.
\item p3 l19: sentence ends with a comma
\item p3 l24: this is an important point that shouldn't be relegated to a parenthetical statement
\item p3 l38: compared "to" the old textbook subset
\item p4 l51: might be better to add "the" before "data cleaning process"
\item p5 l39: two data "sets"
\item p6 l28: comply "with" these rules
\end{itemize}}
\item[Reviewer 1:] \textcolor{violet}{}
\end{description}

* We have made the descriptions of the steps more explicit as follows [LIST OF THE CHANGES]

@@

We agree that this level of precision was not necessary. We have modified Table 2 so percentages are to the nearest 1 percent and total percentage (=100%) is omitted.
